MLH1 data report 

### 2017-10-27 rmd_report.rmd
changes to report file

Currently this section is under construction.
```{r}

colnms = c("mouse", "rep")
ply_data <- df.pasd.mice[df.pasd.mice$mouse == "8oct14_PWD_f8",]
#make this the function that I apply over the mice in the data

>>>>

Currently this section is under construction.
```{r}
colnms = c("mouse", "rep")
ply_data <- df.pasd.mice[df.pasd.mice$mouse == "8oct14_PWD_f8",]
#make this the function that I apply over the mice in the data
